Automatic prostate cancer detection through \acs*{dce}-\acs*{mri} images: all you need is a good normalization

### 2016-08-19 02_methods/methods.tex
Finish the draft for the normalization

Therefore, the offset is estimated by finding the shortest-path to cross the graph using Dijkstra algorithm.
The entry and exiting nodes are set to be the bin with the maximum probability for the first \ac{dce}-\ac{mri} serie and the bin corresponding to the median value for the last \ac{dce}-\ac{mri} serie, respectively.
To ensure a robust estimation of the offset, the process of finding the shortest-path is iteratively repeated by shifting the data and updating the heatmap as well as the graph $\mathcal{G}$.
The procedure is stopped once that the offset found do not change.
In general, this process is not repeated more than 3 iterations.
An example of the offset found using this approach is presented in Fig.\,\ref{fig:estimator}.

\subsubsection{Estimate the dispersion of the voxel intensities}

MSE.

\subsubsection{Parametric curve alignment}

Model using 1 translation and one scale.

>>>>

Therefore, the offset is estimated by finding the shortest-path to cross the graph using Dijkstra algorithm.
The entry and exiting nodes are set to be the bin with the maximum probability for the first \ac{dce}-\ac{mri} serie and the bin corresponding to the median value for the last \ac{dce}-\ac{mri} serie, respectively.
To ensure a robust estimation of the offset, the process of finding the shortest-path is iteratively repeated by shifting the data and updating the heatmap as well as the graph $\mathcal{G}$.
The procedure is stopped once that the offset found do not change.
In general, this process is not repeated more than 3 iterations.
An example of the offset found using this approach is presented in Fig.\,\ref{fig:estimator}.
Finally, each sequence is shifted using this offset.

\subsubsection{Time offset and data dispersion correction}

\begin{figure}
  \centering
  \hspace*{\fill}
  \subfigure[\acs*{rmse} computed for each patient of our dataset.]{\label{fig:rmse}\includegraphics[width=.49\textwidth]{02_methods/figures/rmse.pdf}} \hfill
  \subfigure[\acs*{rmse} after alignment using the curve parametric model.]{\label{fig:rmseal}\includegraphics[width=.49\textwidth]{02_methods/figures/rmse_aligned.pdf}}
  \hspace*{\fill}
  \caption{Illustration of the correction of the time offset and the data dispersion.}
  \label{fig:curveal}
\end{figure}

The next variations to correct are the time offset and the data dispersion.
By computing the \ac{rmse} for each \ac{dce}-\ac{mri}, one can observed these two variations as shown in Fig.\,\ref{fig:rmse}.
Therefore, to correct these variations, we propose to register each patient \ac{rmse} to a mean model which corresponds to the mean of all patients \ac{rmse}.
The parametric model to perform the registration is formulated as in Eq.\,\eqref{eq:model}:

\begin{equation}
  T(\alpha, \tau, f(t)) = \alpha f(t - \tau) ,
  \label{eq:model}
\end{equation}

\noindent where $\alpha$ and $\tau$ are the two parameters handling the time offset and global scale, respectively, $f(\cdot)$ is the \ac{rmse} function.

Therefore the registration problem is equivalent to:

\begin{equation}
  \argmin_{\alpha, \tau} = \sum_{t=0}^{N} \left[ T\left(\alpha, \tau, f(t)\right) - \mu(t) \right]^{2} ,
  \label{eq:cost}
\end{equation}

\noindent where $\mu(\cdot)$ is the mean model, $N$ is the number of \ac{dce}-\ac{mri} serie.

Illustration of the correction applied to each \ac{rmse} patient is shown in Fig.\,\ref{fig:rmseal}.
Once all these parameters have been inferred, the data can be shifted as well as scale.
